Twisted 11-dimensional supergravity

### 2021-10-15 intro.tex

For many years, twisting constructions were motivated by the goal of producing topological field theories, and correspondingly emphasized the role of particular modifications of  Lorentz symmetry via ``twisting homomorphisms'' designed to produce scalar supercharges.
From a more modern perspective, though, twisting a supersymmetric field theory is just a systematic way of taking invariants with respect to a fixed supercharge. This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.\footnote{More generally, one could consider ``omega backgrounds'' by taking the derived invariants of a more general subalgebra in which the odd part is not necessarily abelian.}
The variety of appropriate square-zero elements was studied systematically in~\cite{NV}, and has deep relations not only to the  classification of  twists, but to the construction  of supersymmetric field theories via the pure spinor formalism~\cite{Cederwall,EHSW}. The name ``pure spinor'' originates because the  variety of  square-zero elements always contains a minimal stratum that is related to the space of Cartan pure spinors; in turn, these correspond to choices of complex structure on the  spacetime, at least when the dimension is even. 
As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lfloor d/2\rfloor$ of the translations act nontrivially. Other twists can be understood as further twists of this holomorphic theory.
The importance and interest of holomorphic twists was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite{NekThesis}. (Constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.)

@@

Through the dimensional reduction of our 11-dimensional theory we will find a match with Costello and Li's descriptions of twists of 10-dimensional supergravity in terms of BCOV theory.
In Table \ref{table:IIsugra}, we provide a summary of the conjectural twists of type IIA and type IIB supergravity. 
The notation $\CC^n_B \times \RR^{2m}_A$ uses terminology from the topological string. 
It means that the twist of supergravity we are considering arises from a certain subsector of a hybrid topological string which is the $B$-model into the Calabi--Yau manifold $\CC^n$ and the $A$-model into the symplectic manifold $\RR^{2m}$.

\begin{table}[]
\begin{tabular}{c|c|c|c|c|c|c|c|}
\cline{2-7}
& SU(5) twist & SU(4) twist & SU(3) twist & SU(2) twist & SU(1) twist & top twist  \\ \hline
\multicolumn{1}{|l|}{IIA} & \S \ref{s:su5IIA} & $\CC^4_B \times \RR^2_A$ & & $\CC^2_B \times \RR^6_A$ & $\begin{matrix} \text{perturbatively} \\ \text{trivial} \end{matrix}$ & $\RR^{10}_A$  \\ \hline
\multicolumn{1}{|l|}{IIB} & $\CC^5_B$ & & $\CC^3_B \times \RR^4_A$ & & $\CC_B \times \RR^8_A$ & \\ \hline
\end{tabular} \smallskip
\caption{A summary of twists of 10-dimensional supergravity}
\label{table:IIsugra}
\end{table}

In \S \ref{s:su4red} we will show that the reduction along $\{0\} \times \RR \times \{0\} \subset \CC^4 \times \CC \times \RR$ is equivalent to the $SU(4)$ twist of type IIA supergravity. 
The topological string approach does not lead to a description of the minimal, or holomorphic, twist of type IIA supergravity. 
In \S \ref{s:su5IIA}, we describe the reduction along the line $\{0\} \times \RR \subset \CC^5 \times \RR$ to obtain a conjectural description of the holomorphic $SU(5)$ twist of type IIA supergravity.

>>>>

For many years, twisting constructions were motivated by the goal of producing topological field theories, and correspondingly emphasized the role of particular modifications of  Lorentz symmetry via ``twisting homomorphisms'' designed to produce scalar supercharges.
From a more modern perspective, though, twisting a supersymmetric field theory is just a systematic way of taking invariants with respect to a fixed supercharge. This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.\footnote{More generally, one could consider ``omega backgrounds'' by taking the derived invariants of a more general subalgebra in which the odd part is not necessarily abelian.}
The variety of appropriate square-zero elements was studied systematically in~\cite{NV}, and has deep relations not only to the  classification of  twists, but to the construction  of supersymmetric field theories via the pure spinor formalism~\cite{Cederwall,EHSW}. The name ``pure spinor'' originates because the  variety of  square-zero elements always contains a minimal stratum that is related to the space of Cartan pure spinors; in turn, these correspond to choices of complex structure on the  spacetime, at least when the dimension is even. 
As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lceil d/2\rceil$ of the translations act nontrivially. Other twists can be understood as further twists of this holomorphic theory.
The importance and interest of holomorphic twists was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite{NekThesis}. (Constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.)

@@

Through the dimensional reduction of our 11-dimensional theory we will find a match with Costello and Li's descriptions of twists of 10-dimensional supergravity in terms of BCOV theory.
In Table \ref{diagram}, we provide a summary of the comparisons with twists of supergravity in lower dimensions we perform. The squigly arrows denote further twists, and the solid arrows denote various kinds of reductions.

\begin{center}
\begin{tikzcd}[row sep=large]
                                                                         &  \parbox{3cm}{\centering minimal twist of 11d} \arrow[ld, "\text{topological }S^1" '] \arrow[d, "\text{slab }" '] \arrow[rdd, "\text{CY3}" ' pos=.75] \arrow[rr, rightsquigarrow] \arrow[rd, "\text{holomorphic }S^1"] &                                                             &  \parbox{3cm}{\centering non-minimal twist of 11d} \arrow[d, "\text{topological }S^1"] \\
 \parbox{3cm}{\centering minimal twist of type IIA} \arrow[r, "\text{orbifold}"] &  \parbox{3cm}{\centering minimal twist of type I} \arrow[r, rightsquigarrow, crossing over]                                                                                                                                                                                               &  \parbox{3cm}{\centering SU(4) twist of type IIA} \arrow[r, rightsquigarrow] &  \parbox{3cm}{\centering SU(2) twist of type IIA}                                                 \\
                                                                         &                                                                                                                                                                                                                                                          & \parbox{3cm}{\centering minimal twist of 5d $\cN=1$}                   &                                                                                                
\end{tikzcd}
\end{center}
\label{diagram}

In \S \ref{s:su4red} we will show that the reduction along $\{0\} \times \RR \times \{0\} \subset \CC^4 \times \CC \times \RR$ is equivalent to the $SU(4)$ twist of type IIA supergravity. 
The topological string approach does not lead to a description of the minimal, or holomorphic, twist of type IIA supergravity. 
In \S \ref{s:su5IIA}, we describe the reduction along the line $\{0\} \times \RR \subset \CC^5 \times \RR$ to obtain a conjectural description of the holomorphic $SU(5)$ twist of type IIA supergravity. 
In \S \ref{s:Ired}, we show that the reduction along the interval $\{0\}\times [0,1]\subset \CC^5\times [0,1]$ with certain boundary conditions on the endpoints of the interval is equivalent to the twist of type I supergravity. We further observe in \S \ref{s:orbifold} that the twist of type I arises as the fixed points of a natural $\ZZ/2$ action on the minimal twist of IIA. Next, in \S \ref{s:CY3} we study the reduction along a Calabi-Yau 3 fold to obtain a conjectural description of the minimal twist of 5d $\cN=1$ supergravity. Finally, we show in \S \ref{s:nonmin} how the non-minimal twist of 11d supergravity arises as a further twist of our holomorphic twist.
